Tax-Equity-in-Low-and-Middle-Income-Countries-Replication

### 2024-02-16 paper/paper.qmd
Refactor the folders and update scripts

## Figure 1
```{r}
source("../scripts/99-replications-figure1.R")
```

## Figure 2
```{r}
source("../scripts/100-replications-figure2.R")
```

>>>>

## Figure 1
```{r}
#| label: fig-taxes-gdp
#| fig-cap: Relationship between tax revenue and gdp per capita
#| echo: false
#| warning: false
#| message: false
source("../scripts/99-replications-figure1.R")
```

## Figure 2
```{r}
#| label: fig-difficulty-gdp
#| fig-cap: Relationship between the difficulties of collecting taxes and gdp per capita
#| echo: false
#| warning: false
#| message: false
source("../scripts/100-replications-figure2.R")
```

## Figure 4
```{r}
#| label: fig-tax-rate-gdp
#| fig-cap: Relationship between the tax rate and gdp per capita
#| echo: false
#| warning: false
#| message: false
source("../scripts/101-replications-figure4.R")
```
